Meta-analysis Manuscript Wrangling

### 2021-07-14 shared analysis files /manuscript_datavis_22jun21.Rmd
adding in broader response columns for additional figures

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_acclim_ES<-dat_acclim_ES %>% 
  filter (!is.na(yi)) 
```

@@

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_full_var_ES<-dat_full_var_ES %>% 
  filter (!is.na(yi)) 
```
# Motivation and Hypotheses

@@

count(dat_acclim_ES, resp_units)
count(dat_full_var_ES, resp_units)

dat_acclim_ES %>%

@@

>>>>

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_acclim_ES<-dat_acclim_ES %>% 
  filter (!is.na(yi)) %>%
  mutate(metric = case_when(resp_def %in% c("log CO2 production", 
                                            "maximal swimming speed", 
                                            "Maximum burst swim speed", 
                                            "Oxygen consumption", 
                                            "Performance breadth (Tbr)",
                                            "Time to heat knockdown",
                                            "Scope of thermal tolerance (CTmax - CTmin)",
                                            "RMR", 
                                            "Speed", "Thermal preference", 
                                            "Topt", "Tpref", 
                                            "Ucrit", "Umax") ~ "Pmax",
                            resp_def %in% c("CTmin", "LTmin") ~ "CTmin",
                            resp_def %in% c("CT max", "CTmax", "LTmax", "ULT50") ~ "CTmax",
                            resp_def %in% c("LDH activity", "CCO activity", 
                                            "CS activity") ~ "Biochemical"
                            ))
```

@@

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_full_var_ES<-dat_full_var_ES %>% 
  filter (!is.na(yi)) %>%
  mutate(metric = case_when(resp_def %in% c("abdomen length", "adult weight", 
                                            "blade length/total leaf length", 
                                            "body length", "body mass", "body size", 
                                            "body weight", "carapace height", 
                                            "carapace width", 
                                            "final length", "final mass",
                                            "fore-limb length", 
                                            "group mean body weight", 
                                            "head length", "head width", 
                                            "hind-limb length", 
                                            "hypocotyl length", "mass", 
                                            "maximal length", 
                                            "snout-vent length", "tail length",
                                            "total length", 
                                            "wing centroid", "body (centroid) size", 
                                            "egg mass", "ovary mass, dry", 
                                             "testes mass, dry", 
                                             "pupal shell weight", "pupal weight") ~ "size", 
                            resp_def %in%  c("average cumulative number of eggs laid per female",
                                             "hatching success", 
                                             "offspring per mating",
                                             "total offspring", 
                                             "percent females") ~ "fecundity",
                            resp_def %in% c("Adult eclosion to death", 
                                            "dessication tolerance", 
                                            "egg to adult viability",
                                            "infestation rate", 
                                            "Mortaility", 
                                            "Parasitism success", 
                                            "startvation tolerance", 
                                            "success of parasitism", 
                                            "survival", "Survival", 
                                            "Larval mortaility", "longevity") ~ "survivorship", 
                            resp_def %in% c("aquatic speed", 
                                            "daily energy expenditure", 
                                            "distance covered", 
                                            "Energy consumption", 
                                            "feeding efficiency", 
                                            "feeding rate", ,
                                            "RMR", "sprint speed",
                                          "Sqrt Cellular energy allocation (CEA)", 
                                            "Sqrt of available energy", 
                                          "population growth rate","productivity", 
                                             "rate of change", 
                                             "specific growth rate") ~ "energetics", 
                            resp_def %in% c("development time", 
                                            "development to stages 35-37", 
                                            "days to first slough", 
                                            "developmental time", 
                                            "egg to adult", 
                                            "egg to pupa", "incubation period", 
                                            "median days to bolt", 
                                            "Third instar to adult", 
                                            "Third instar to pupa") ~ "development", 
                            resp_def %in% c("Catalase", "cortisol",
                                             "Hexokinase", "Hsp70", 
                                            "oxidative damage", 
                                            "Pyruvate kinase", "TAC", 
                                            "SOD", "glucose") ~ "biochemistry"))

count(dat_full_var_ES, metric)
```
# Motivation and Hypotheses

@@

@@

```{r}
g <- dat_full_var_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-2.6,1.7)+
  coord_flip()+
  ggtitle("ASSAY")

h <- dat_acclim_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-2.6,1.7)+
  coord_flip()+
  ggtitle("ACCLIMATION")

h / g
```
